Selective electroporation of the viral envelope

### 2021-03-22 documents/pure_electroporation.tex
README

\title{On selective electroporation of the viral envelope}
\author{\small{Daniel Correia\orcidlink{0000-0002-9353-0216} (therobotist@gmail.com), Ontario, Canada.}}
\date{March 2021}

@@

	\noindent As pulse duration is reduced from the microsecond to nanosecond regime, effects targeting smaller intracellular structures are expected and observed. Indeed, pulses shorter than 10 ns have been observed to porate the nuclear envelope while leaving the cell membrane intact.

	As a followup to

@@

@@

can determine the conductivity sigma from Brackley's kappa debye length

@@

It is usually agreed that the viral shell has a permittivity of about 60 to 80, similar to the nuclear membrane (60 to 100) but unlike the cell membrane ($\epsilon_r\approx 10$).

>>>>

\title{Selective electroporation of the viral envelope}
\author{\small{Daniel Correia\orcidlink{0000-0002-9353-0216} (therobotist@gmail.com), Ontario, Canada.}}
\date{March 2021}

@@

	\noindent As pulse duration is reduced from the microsecond to nanosecond regime, effects targeting smaller intracellular structures are expected and observed. Indeed, pulses shorter than 10 ns have been observed to porate the nuclear envelope and organelle membranes while leaving the cell membrane intact.

@@

As a followup to.

@@

@@

In electrorotation, it is usually found that the viral shell has a permittivity of about 60 to 80, similar to the nuclear membrane (60 to 100) but massively unlike the cell membrane ($\epsilon_r\approx 10$).
